%======================================================
%  SUYESH JADHAV — RESUME
%  Clean single-file build. No spacing hacks.
%  Compiler: pdflatex (Overleaf default)
%======================================================
\documentclass[9pt, letterpaper]{article}

%------------------  PACKAGES  -----------------------
\usepackage[
  top=0.3in, bottom=0.3in,
  left=0.5in,  right=0.5in
]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}           % better text fitting
\usepackage{enumitem}            % list control
\usepackage{titlesec}            % section formatting
\usepackage{hyperref}            % links
\usepackage{xcolor}              % colors
\usepackage{parskip}             % paragraph spacing

%------------------  HYPERLINK STYLE  ----------------
\hypersetup{
  colorlinks = true,
  urlcolor   = black,
  linkcolor  = black
}

%------------------  GLOBAL SPACING  -----------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\raggedbottom
\raggedright

%------------------  SECTION FORMAT  -----------------
% Before: 8pt  |  After rule: 4pt  — consistent for all sections
\titleformat{\section}
  {\scshape\raggedright\large}
  {}{0em}{}
  [\color{black}\titlerule]
\titlespacing*{\section}{0pt}{4pt}{2pt}

%------------------  CUSTOM COMMANDS  ----------------

% Outer list: wraps subheadings and project headings
\newcommand{\outerListStart}{
  \begin{itemize}[
    leftmargin = 0pt,
    label      = {},
    topsep     = 1pt,
    itemsep    = 2pt,
    parsep     = 0pt
  ]
}
\newcommand{\outerListEnd}{\end{itemize}}

% Inner list: wraps bullet points under each entry
\newcommand{\bulletListStart}{
  \begin{itemize}[
    leftmargin = 12pt,
    label      = \textbullet,
    topsep     = 1pt,
    itemsep    = 0pt,
    parsep     = 0pt
  ]
}
\newcommand{\bulletListEnd}{\end{itemize}}

% Single bullet item
\newcommand{\bitem}[1]{
  \item \small #1
}

% Experience / Education subheading: 4 args
%   #1 Company/School  #2 Date
%   #3 Role/Degree     #4 Location
\newcommand{\subheading}[4]{
  \item
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \small #2 \\
    \textit{\small #3} & \textit{\small #4}
  \end{tabular*}
  \vspace{-2pt}
}

% Project heading: 2 args
%   #1 Title | Tech stack   #2 Date
\newcommand{\projectheading}[2]{
  \item
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \small #1 & \small #2
  \end{tabular*}
  \vspace{-6pt}
}

%======================================================
\begin{document}
%======================================================

%------------------  HEADER  -------------------------
\begin{center}
  {\LARGE \textbf{Suyesh Jadhav}}\\[4pt]
  \small
  +1-984-382-2189
  $\,|\,$
  \href{mailto:smjadha2@ncsu.edu}{smjadha2@ncsu.edu}
  $\,|\,$
  \href{https://linkedin.com/in/suyeshjadhav}{linkedin.com/in/suyeshjadhav}
  $\,|\,$
  \href{https://github.com/SuyeshJadhav}{github.com/SuyeshJadhav}
\end{center}

\vspace{1pt}

%------------------  PROFESSIONAL SUMMARY  -----------
\section{Professional Summary}

\small
Results-driven Computer Science graduate student specializing in intelligent systems and scalable architecture. Adept at building complex tools, including locally hosted AI assistants and network diagnostic software, with a strong focus on engineering efficiency.

%------------------  EDUCATION  ----------------------
\section{Education}

\outerListStart

  \subheading
    {North Carolina State University (NCSU)}{August 2025 -- May 2027}
    {Master of Computer Science (MCS) $|$ GPA: 3.7/4.0}{Raleigh, NC}

  \subheading
    {K.J. Somaiya College of Engineering}{August 2021 -- May 2025}
    {B.Tech in Computer Engineering $|$ CGPA: 9.05/10.0}{Mumbai, India}

\outerListEnd

%------------------  TECHNICAL SKILLS  ---------------
\section{Technical Skills}

%% BEGIN SKILLS %%
\outerListStart
  \item \small
  \textbf{Languages:}
    Python, Go, Java, C++, JavaScript/TypeScript, SQL, Dart \\[2pt]
  \textbf{Mobile \& Web:}
    ReactJS, Node.js, Express.js, FastAPI, Spring Boot,
    React Native, Flutter, HTML/CSS \\[2pt]
  \textbf{Cloud \& DevOps:}
    Firebase, Docker, GitHub Actions (CI/CD), Linux, Git \\[2pt]
  \textbf{Databases \& Tools:}
    MongoDB, PostgreSQL, SQLite, ChromaDB, TensorFlow, NLP
\outerListEnd
%% END SKILLS %%

%------------------  PROJECTS  -----------------------
\section{Projects}

\outerListStart

  % --- Project 1 ---
  \projectheading
    {\textbf{Personal AI Agent}
     $\,|\,$ \textit{Python, FastAPI, SQLite, ChromaDB, Ollama, React Native}}
    {Oct 2025 -- Feb 2026}
  \bulletListStart
  %% BEGIN PROJECT: Personal AI Agent %%
    \bitem{Independently designed a personal AI agent from scratch to
           solve daily-life tasks --- growing from a location-aware
           grocery reminder into a full \textbf{ReAct reasoning system}
           with persistent memory, voice I/O, calendar integration,
           and a cross-platform mobile frontend.}
    \bitem{Architected a \textbf{6-tool ReAct agent runtime} with
           decorator-based auto-registration extracting docstrings and
           type hints at registration time, enforcing parameter
           coercion and loop-detection guards across 9 intent
           categories to eliminate infinite reasoning cycles across
           20+ API endpoints.}
    \bitem{Engineered a \textbf{hybrid memory layer} combining SQLite
           (2.61ms avg retrieval, sub-3ms P95 via 15+ indexes and WAL
           journaling) with ChromaDB vector search (190ms over
           384-dimensional embeddings) for structured and context-aware
           recall at 1,000+ row scale.}
    \bitem{Implemented an adaptive \textbf{personality engine} tracking
           communication style, verbosity preferences, and topic
           affinities --- learning from user corrections via a feedback
           table and serving cached profiles under a 5-minute TTL for
           low-latency personalization.}
  %% END PROJECT: Personal AI Agent %%
  \bulletListEnd

  % --- Project 2 ---
  \projectheading
    {\textbf{WolfCafe+ -- Full-Stack Dining Platform}
     $\,|\,$ \textit{React, Node.js, MongoDB, Socket.IO, GitHub Actions}}
    {Aug 2025 -- Dec 2025}
  \bulletListStart
  %% BEGIN PROJECT: WolfCafe+ %%
    \bitem{Led backend development in a 3-person team, independently
           architecting the \textbf{ML recommendation engine} and
           \textbf{admin analytics dashboard} within a platform
           exposing 45+ REST endpoints secured via JWT and
           role-based access control.}
    \bitem{Built a \textbf{hybrid recommendation engine} combining
           collaborative filtering, content-based similarity, temporal
           scoring, and popularity signals (weights 0.4/0.3/0.2/0.1)
           with 20\% exploration injection and per-category
           diversity capping.}
    \bitem{Implemented \textbf{MongoDB aggregation pipelines} for
           admin analytics (items sold, time-series trends, top-5
           products) with zero-fill for missing dates, benchmarked
           at \textbf{2.17ms average API response} across 100
           iterations.}
    \bitem{Engineered real-time group ordering via \textbf{Socket.IO}
           room broadcasts --- HTTP response returned first, with email
           and socket notifications dispatched asynchronously ---
           supporting 6-char share codes and 2-hour session expiry.}
  %% END PROJECT: WolfCafe+ %%
  \bulletListEnd

  % --- Project 3 ---
  \projectheading
    {\textbf{TweetScape -- Social Media Analytics Platform}
     $\,|\,$ \textit{React 19, FastAPI, D3.js, Transformers, SQLite}}
    {December 2025}
  \bulletListStart
  %% BEGIN PROJECT: TweetScape %%
    \bitem{Engineered a \textbf{10-stage NLP pipeline} orchestrating
           data ingestion, deduplication, semantic embedding, and
           sentiment clustering to process social media data
           end-to-end at \textbf{75ms per tweet}.}
    \bitem{Orchestrated a \textbf{5-model inference stack} ---
           SentenceTransformers (484 texts/sec), RoBERTa sentiment,
           DistilRoBERTa emotion, KeyBERT, and TF-IDF clustering ---
           reduced to 2D via UMAP for interactive visualization.}
    \bitem{Built a \textbf{React 19 + D3 force-directed simulation}
           mapping sentiment polarity to spatial positioning with
           collision physics, glow effects for high-polarity nodes
           ($|$score$|>0.7$), and hover tooltips.}
    \bitem{Implemented \textbf{SQLite query-result caching} with
           24-hour TTL and LLM-powered query expansion via Ollama
           Gemma, short-circuiting redundant scraping and model
           inference on repeated topics.}
  %% END PROJECT: TweetScape %%
  \bulletListEnd

\outerListEnd

%------------------  EXPERIENCE  ---------------------
\section{Experience}

\outerListStart

  \subheading
    {KJSCE Software Development Cell}{March 2024 -- August 2024}
    {Software Engineering Intern}{Mumbai, India}
  \bulletListStart
    \bitem{Architected and delivered a \textbf{full-stack} online
           learning platform serving \textbf{1,000+ students and
           faculty} using \textbf{React, Node.js, Express, and
           MongoDB (MERN)}, owning authentication, course management,
           and admin dashboard end-to-end.}
    \bitem{Diagnosed \textbf{API} routing bottlenecks and redesigned
           \textbf{MongoDB} indexing strategy, reducing CRUD response
           times by \textbf{40\%} and improving database query
           throughput.}
    \bitem{Implemented modular \textbf{React} UI components for
           course creation, content upload, and role-based access
           control, improving workflow clarity for faculty users.}
  \bulletListEnd

  \subheading
    {Caarya Innovative Solutions Pvt. Ltd.}{December 2023 -- February 2024}
    {Software Development Intern}{Mumbai, India}
  \bulletListStart
    \bitem{Built a \textbf{full-stack B2B e-commerce platform} for a
           dental wholesale client featuring a product catalog,
           order placement, and order tracking system using
           \textbf{[your stack: e.g., React, Node.js, MySQL]}.}
    \bitem{Developed an \textbf{admin dashboard} with analytics views
           backed by \textbf{RESTful APIs} and \textbf{MySQL},
           enabling real-time visibility into orders and
           inventory for business stakeholders.}
  \bulletListEnd

\outerListEnd

%======================================================
\end{document}